\cvsection{Pro}{fessional Experience}
\begin{cventries}
  \cventry
    {C\# .NET Apprentice}
    {The Software Guild}
    {Minneapolis, MN}
    {May 2017 - July 2017}
    {
      \begin{cvitems}
       \item {Rigorous apprenticeship program focusing on C\# .NET MVC full-stack web development.}
       \item {Built a single-page vending machine web application, utilizing bootstrap, CSS and JavaScript for a fluid user experience.}
       \item {Developed a C\# console application for a flooring company that reads and saves data in CSV format and uses interfaces with ninject dependency injection for unit testing.}
       \item {Worked on a team to develop a Windows application game as an extra-curricular project.}
       \item {Designed a weather forecast web application, using Ajax to pull data from an online API for an entered postal code.}
	\item {Created SQL database schema for a Hotel Reservation System, to track room configurations, individual reservations and extra charges, customer invoices and promotional codes.}
	\item {Competed development of a College Student information system using ASP .NET MVC, implementing the ability to add, edit and delete student information, along with server side validation of data.}
      \end{cvitems}
    }{}{}


  \cventry
    {HighJump Warehouse Systems Developer}
    {WYNIT Distribution, LLC}
    {Eden Prairie, MN}
    {July 2012 - May 2017}
    {
      \begin{cvitems}
       \item {Lead new implementation of HighJump WMS 12.8 with others. Migration of legacy processes to help streamline implementation (SAP interface, Warehouse Control System (WCS) interface).  Project included development of product serial number scanning in all warehousing processes.}
       \item {Using RedGate SQL tools to monitor performance, implemented performance enhancements which immediately reduced SQL Server CPU usage by 80\%}
       \item {Architected and developed new processes for ConnectShip application integration from a depreciated interface.}
       \item {Designed and built socket based communication with a third-party Warehouse Control System (WCS) to divert picks within zones, validate container weights and dictate the sortation of containers to shipping lanes. Including creation of detailed documentation of the communication to occur between the systems.}
       \item {Configured changes to replenishment process to reduce orders waiting on product, nearly doubling the quantity of orders being picked by reducing the time lost by picking staff.}
       \item {Assisted in execution of moving primary warehouse from Minnesota to Texas, and later Texas to Tennessee. Including additional development to warehouse system processes due to differences in operations between warehouses.}
       \item {Developed and supported changes to HighJump Warehouse system integrated to SAP and conveyance/voice picking warehouse control system.}
      \end{cvitems}
    }
   {(formerly Navarre Corporation)}
   {(December 2006 - May 2017)}





  \cventry
    {Warehouse Lead}
    {}
    {}
    {September 2011 - July 2012}
    {
      \begin{cvitems}
       \item {Supervised and trained a team of up to 8 forklift/stockpicker operators in the areas of inventory replenishment and product movement.}
       \item {Consulted on and performed specialized shipping projects in an effort to provide customers with the highest level of service and shipping optimization.}
      \end{cvitems}
    }{}{}




  \cventry
    {Shipping Specialist}
    {}
    {}
    {December 2006 - September 2011}
    {
      \begin{cvitems}
       \item {Inspected incoming and outgoing shipments to ensure product met specifications and tracked inventory through warehouse management system.}
       \item {Accurately and efficently prepared orders by printing labels and shipping documents, picking and packing the product, and verifying order correctness.}
       \item {Performed the loading and unloading of product with a focus on maintaining product integrity and positive workflows.}
      \end{cvitems}
    }{}{}


\end{cventries}